Programming Language Survey Paper on Haskell

### 2013-04-22 projects/term_paper/paper.tex
Fixed a small typo in a code example.
Edits through 2.1.2, and fixed some code examples.

\begin{minted}{haskell}
let x = 2
let pi = 3.14
let c = 'c'
let isHaskellAwesome = true
\end{minted}

Two more essential data types in Haskell are lists and tuples. Lists are the most used data type due to their expendability 
and the wide range of functions that are available to manipulate them. They can easily be created, traversed, concatenated, 
reversed, sorted, and more with standard, built-in functions. Lists, however, are homogeneous and can only contain elements 
of the same data type. Tuples, on the other hand, can be heterogeneous. They are useful when the types and exact number of 
values to be combined are known. Like lists, tuples also comes with a surplus of built-in functions, one of which is the 
ability to zip two lists into one by joining matching elements into pairs. Simple yet elegant code can be written which 
combines the attributes of lists, tuples, and the other various other data types in Haskell.

@@

Haskell also allows the definition Strings, which are represented by surrounding text with double quotes. Strings, however, 
are not actually a data type. Although they can be initialized using the double quote syntax, the compiler converts the 
string into a list of characters at compile time. The use of the String notation is simply syntatic sugar for programmers. 
It also helps increase the readability of code. In the following example, the data is stored in the representation of 
str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in str2, 
which is much more understandable.

\begin{minted}{haskell}
let str1 = ['H','a','s','k','e','l','l','!']
let str2 = "Haskell!"
\end{minted}

In addition to these basic data types, Haskell also offers type variables. Type variables are variables whose type has 
not been explicitly declared; rather, they can be any type. By defining a function without declaring data types, the 
variables in the function can be used as any type and the function can be polymorphic. In the following example, the 
function can handle a list of any type because its uses a type variable.

>>>>

\begin{minted}{haskell}
let x = 2
let pi = 3.14
let c = 'c'
let isHaskellAwesome = True
\end{minted}

Two more foundational data types in Haskell are lists and tuples. Lists are the most used data type due to their expendability 
and the wide range of functions that are available to manipulate them. They can easily be created, traversed, concatenated, 
reversed, sorted, and more with standard, built-in functions. Lists, however, are homogeneous, ordered collections of
similar data types. Tuples, on the other hand, heterogeneous collections. Tuples are most useful when the types and exact number of 
values to be combined are known. Like lists, there is a wide array of built-in functions for tuples including, for instance,
a function for zipping two lists into one by joining matching elements into tuples. Simple yet elegant code can be written by
employing lists, tuples, and the other various other data types in Haskell.

@@

Haskell also allows the definition Strings, which are represented by surrounding text with double quotes. Strings, however, 
are not their own data type. Although string literals can be initialized using the double quote syntax, the compiler converts the 
string into a list of characters at compile time. The use of the String notation is simply syntatic sugar for programmers. 
It also helps increase the readability of code. In the following example, the data is stored in the representation of 
str1: a list of characters. However, Haskell allows the definition of a string using double quotes, as seen in \texttt{str2}, 
which is much more understandable.

\begin{minted}{haskell}
let str1 = ['H','a','s','k','e','l','l','!']
let str2 = "Haskell!"   -- shorthand for str1
\end{minted}

In addition to these basic data types, Haskell also offers type variables. Type variables are variables whose type has 
not been explicitly declared; rather, they can be any type.  By defining a function without declaring data types, the 
variables in the function can be used as any type thereby enabling polymorphic behaviors. In the following example, the 
function can handle a list of any type because its uses a type variable.
